In summary, we described a data-driven method to estimate the $WW$ 
jet-veto signal efficiency and its systematic uncertainties. 
The $WW$ jet-veto efficiency in data is parametrized as the product 
of the $Z$ jet-veto efficiency in the data and the $WW/Z$ jet-veto efficiency 
in the MC. 

We have measured the $Z$ jet-veto efficiencies in data and 
compared to various MC samples, shown in 
Table~\ref{tab:zeff_results}-\ref{tab:zeff_jec_results}. 
We observed good agreement of $Z$ jet-veto efficiency 
between data and the Pythia and Madgraph MC samples. 
%The jet-veto efficiency predicted by the MC@NLO MC is statistically 
%smaller than the values predicted by the Pythia and Madgraph MC. 
We have studied the $WW/Z$ jet-veto efficiency ratios using the 
Pythia, Madgraph and MC@NLO MC samples. 
The predictions from the Madgraph and MC@NLO MC samples are 
found to agree with each other within 1\%. 
The jet energy spectrum in the Pythia MC is however significantly softer 
than the other two, yielding a difference of more than 10\% at 
the jet \pt cut of 20 GeV. 
Based on the above findings, we choose the Madgraph as the 
nominal MC to calculate the $WW/Z$ jet-veto efficiency ratio 
and assign half of the difference between the Pythia and Madgraph 
predictions as the $R_{WW/Z}^{MC}$ uncertainties. 
%This large difference is likely due to the 
%account for the large angle initial state radiation 

The $WW$ jet-veto efficiencies using the uncorrected and 
corrected PFJet at \pt cut of (20, 25, 30) GeV are tabulated 
in Table~\ref{tab:wweff_results}-\ref{tab:wweff_jec_results}. 







%%%% Need a table for the final results

%%%%%%%%%%%%%%%%%%%%%5
\begin{table}[htbp]
\caption{Jet-veto signal efficiency on $WW$ using the uncorrected PFJet. Madgraph MC is chosen 
for the $R_{WW/Z}^{MC}$}
\begin{center}
\label{tab:wweff_results}
\begin{tabular}{c|cc|c}
\hline
\hline
Jet-veto Cut (GeV) & $\epsilon_Z^{data}$ (\%) & $R_{WW/Z}^{MC}$ (\%) & $\epsilon_{WW}$ (\%) \\
    20 &   76.3$\pm$ 1.0 &   76.3$\pm$ 0.7$\pm$ 6.2 &   58.3$\pm$ 0.9$\pm$ 4.8 \\
    25 &   82.6$\pm$ 0.9 &   79.1$\pm$ 0.6$\pm$ 4.9 &   65.4$\pm$ 0.9$\pm$ 4.1 \\
    30 &   87.2$\pm$ 0.8 &   80.9$\pm$ 0.6$\pm$ 4.2 &   70.5$\pm$ 0.8$\pm$ 3.7 \\
\hline
\hline
\end{tabular}
\end{center}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%5
%\begin{table}[htbp]
\caption{Jet-veto signal efficiency on $WW$ using the L2L3 corrected PFJet for both data and MC. 
For data, additional residual correction is applied as well. 
Madgraph MC is chosen for the $R_{WW/Z}^{MC}$}
\begin{center}
\label{tab:wweff_jec_results}
\begin{tabular}{c|cc|c}
\hline
\hline
Jet-veto Cut (GeV) & $\epsilon_Z^{data}$ (\%) & $R_{WW/Z}^{MC}$ (\%) & $\epsilon_{WW}$ (\%) \\
    20 &   71.3$\pm$ 1.1 &   74.9$\pm$ 0.7$\pm$ 6.5 &   53.4$\pm$ 1.0$\pm$ 4.6 \\
    25 &   78.8$\pm$ 1.0 &   77.5$\pm$ 0.7$\pm$ 5.7 &   61.1$\pm$ 0.9$\pm$ 4.5 \\
    30 &   84.5$\pm$ 0.9 &   79.7$\pm$ 0.6$\pm$ 4.8 &   67.3$\pm$ 0.9$\pm$ 4.1 \\
\hline
\hline
\end{tabular}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%5
