For the cross section measurement of $pp\to WW\to 2l 2\nu_l$
~\cite{wwanalysis}, one of the dominant backgrounds is the top-background. 
The main difference between the top-background and $WW$ signal is the 
presence of one or two extra $b$-jets in the final states. Thus, one 
efficienct way to suppress the top-background is to apply 
jet-veto, vetoing the events with leading jet \pt\, above a thresold at a 
given $\eta$ range. The specific \pt\, thresolds and the $\eta$ 
ranges are discussed in this note. 
%In $WW$ analysis, we choose 25 GeV as the working point. 

The jet-veto efficiency of $WW$ can not be measured directly 
from the data. We have to use the MC to certain extent. 
%signal needs to be carefully evaluated 
%for $WW$ cross section measurement. 
In this note, we describe a partially data-driven approach to 
measure $WW$ jet-veto signal effcicieny in data. 
In this approach, we use the well-defined process 
$pp\to Z\to 2l$ as a control region to test the agreement 
in the jet spectrum between data and MC. 
We then estimate the jet-veto signal efficiency on $WW$ as the 
jet-veto efficiency of $pp\to Z\to 2l$ on data multiplied 
by the $WW/Z$ jet-veto efficiency ratio estimated on the Monte Carlo, 
shown in Equation~\ref{eq:wweff}. 
Table~\ref{tab:datasets} summarizes the data and MC samples used in this note. 

The uncertainties of jet-veto signal efficiency come from 
both the matrix element calculations % uncertainties and 
and the jet reconstruction. %uncertainties. 
In the leading order matrix element calculation, 
the $pp\to WW\to 2l2\nu$ process does not contain jet.
Extra jets are primarily due to the initial 
state radition. It makes the jet energy spectrum 
sensitive to the corrections beyond the LO. 
We could estimate this systematic error by 
comparing the predictions from various MC generators, 
such as, the Pythia, Madgraph and the MC@NLO. 
On the jet reconstruction side, the effects from the jet energy correction 
and its uncertainties can propagate towards the jet-veto efficiency 
estimation as well. Validation of the jet response between the 
data and MC is thus required.

The note is organized as follows. In section~\ref{sec:zeff}, we discuss the jet-veto 
efficiency measurement on $Z$ data, in which 
the choice of the jet-veto $\eta$ region is examined. 
In section~\ref{sec:wwzratio}, we describe the $WW/Z$ jet-veto 
efficiency ratio estimate and its uncertainties. 
In section~\ref{sec:jetresponse}, we discuss the effect of the 
jet energy response to the results. Finally, in section~\ref{sec:conclusion}, 
we present the jet-veto efficiency measurement for $WW$ in data. 


%%%%%%%%%%%%%%%%%%%%%%%
\begin{eqnarray}
\epsilon_{WW}^{data} 
%\equiv {\epsilon_Z^{data}} \times {\frac{\epsilon_{WW}^{data}}{\epsilon_Z^{data}}} 
\approx {\epsilon_Z^{data}} \times ({\epsilon_{WW}^{MC}}/{\epsilon_Z^{MC}}) = {\epsilon_Z^{data}} \times R_{WW/Z}^{MC}  
\label{eq:wweff}
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%5
\begin{table}[htbp]
\caption{List of datasets} 
\begin{center}
\label{tab:datasets}
\begin{tabular}{c|c}
\hline
\hline
\multicolumn{2}{c}{Collision Data} \\ 
Luminosity & Dataset \\ %& nEvents & note \\
\hline
\vspace{-3mm}   &    \cr
\multirow{5}{*} {3.1} & /EG\_Run2010A-PromptReco-v4\_RECO/ \\
& /EG\_Run2010A-PromptReco-v4\_RECO/ \\
& /EG\_Run2010A-Jul16thReReco-v2\_RECO/ \\
& /EG\_Run2010A-Jun14thReReco\_v1\_RECO/ \\
& /MinimumBias\_Commissioning10-SD\_EG-Jun14thSkim\_v1\_RECO/ \\
\hline
\multicolumn{2}{c}{Monte Carlo} \\
\hline
\multirow{3}{*} {Pythia} & /Zee\_Spring10-START3X\_V26\_S09-v1/\\ 
& /Zmumu\_Spring10-START3X\_V26\_S09-v1/\\ 
& /WW\_Spring10-START3X\_V26\_S09-v1 \\ \hline
\multirow{2}{*} {Madgraph} & /ZJets-madgraph\_Spring10-START3X\_V26\_S09-v1 \\
& /VVJets-madgraph\_Spring10-START3X\_V26\_S09-v1/ \\ \hline
\multirow{2}{*} {MC@NLO} & /Zgamma\_ee\_M20-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /Zgamma\_mumu\_M20-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoEE-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoEPlusMuMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoEPlusTauMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoMuMu-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoMuPlusEMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoMuPlusTauMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoTauTau-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoTauPlusEMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
& /WWtoTauPlusMuMinus-mcatnlo\_Spring10-START3X\_V26\_S09-v1/ \\
\hline
\hline
\end{tabular}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%5
